The mzsql project

### 2025-03-19 README.qmd
Adding manuscript figures to README

@@

@@

Converters from mzML to SQLite and DuckDB are currently available in the [converters folder](converters) for R and Python with Julia and C++ hopefully soon. Code from the associated script can be directly copied and pasted into your workflow, though you're responsible for managing the dependency installations.

The database format is shown in the graphic below:

@@

library(ggplot2)
ggplot(pre_data, aes(x=premz, y=int)) +
  geom_point() +
  geom_segment(aes(xend=premz, yend=0)) +
  facet_wrap(~filename, ncol=1)
```

@@

>>>>

![](README_files/figure-manual-manuscript/db_fig.png)

@@

![](README_files/figure-manual-manuscript/singlefile_fig.png)

*Comparison of existing MS file types in query timing and size on disk. Six different queries were tried here: extracting an MS1 or MS2 scan (A and D), a chromatogram (B), all data points within a retention time range (C), or fragment/precursor data (E and F). Thirteen different parsers were implemented in Python for this comparison, visible in the manuscript_things branch of this repository.*

@@

Converters from mzML to SQLite and DuckDB are currently available in the [converters folder](converters) for R with Python, Julia, and C++ hopefully soon. Code from the associated script can be directly copied and pasted into your workflow, though you're responsible for managing the dependency installations.

@@

library(ggplot2)
ggplot(pre_data, aes(x=premz, y=int)) +
  geom_point() +
  geom_segment(aes(xend=premz, yend=0)) +
  facet_wrap(~filename, ncol=1) +
  scale_y_log10()
```

@@

-----

README last built on `r Sys.Date()`
